---
title: "WC Fst from ms"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), '~/Desktop/git/msrFST/', 'README.md')) })
output:
  md_document:
    variant: markdown_github

---
I made use of [Vince Buffalo's msr](https://github.com/vsbuffalo/msr) and added my own function to estimate [Weir & Cockerham’s Fst](http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0135368). This is a work-in-progress to estimate Fst between 2 population comparisons from ms and compare it to an observed distribution. 




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Make an ms run
This can be done through Vince's ms() option (see below) or through stand-alone. Here, I've run the example below. This begins with 1 population that splits into 3 independant populations in 2 generations (2 pops with 100 and 1 with 635). The split is maintained for 3 generations. It outputs 2000 regions that are 100000 bp for 84 diploid samples and assumes a recombination rate of r = 22cm/Mb. 

```{sh}
#./ms 84 2000 -t .254 -I 3 24 32 28 -n 2 0.16 -n 3 0.16 -ej 0.0012 2 1 -ej 0.0012 3 1 -r 56 100000 > testout100r2pops
```


### Load libraries

```{r,include=FALSE, cache=FALSE}
library('devtools')
library('roxygen2')
library('purrr')
library('dplyr')
```
### Build and install msrFST
```{r}
setwd('/Users/brcok/Desktop/git/msrFST')
document()
setwd('/Users/brcok/Desktop/git/')
install('msrFST')
library('msrFST')
setwd('~/Desktop/git/msrFST/')
```

### Load the ms data and calculate fst for each window 
```{r}
getwd()
x <- readLines('testout100r2pops')
y <- parse_ms(x)
inp = (y[which(y$segsites > 1),])
head(inp)
x <- (inp$gametes[1])
fst.lis <- map_dbl(inp$gametes, fst)
head(fst.lis)
#this is FST between 2 populatuions and the founding population 
```

### Compare this to real data 
```{r}
#load a data set of real data - here 3 pops Fst between 2 small and 1 large mai 
fst.all <- read.table('pop1_vs_pop2_100000.windowed.weir.fst',header=T,colClasses = c('character', 'numeric', 'numeric', 'numeric', 'numeric', 'numeric'))

#clean the data a bit
fst.obs <- fst.all$MEAN_FST[fst.all$N_VARIANTS > 1]
fst.obs[fst.obs < 0 ] = 0
fst.lis[fst.lis < 0 ] = 0
fst.lis <- fst.lis[fst.lis>0]
fst.obs <- fst.obs[fst.lis>0]

#plot it
boxplot(fst.obs, fst.lis, notch=T)

#summarize the simulated
summary(fst.lis)

#summarize the observed
summary(fst.obs)

```






